---
title: "Summarising results from simulation 2"
output:
  html_document:
    df_print: paged
    keep_md: true
  pdf_document: default
---

```{r loading, echo=FALSE}
# loading data
# ztoipoisson
ztoi_p_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoipoisson_early_results_point_est"), row.names = 1)
ztoi_p_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoipoisson_early_results_normalL"), row.names = 1)
ztoi_p_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoipoisson_early_results_normalU"), row.names = 1)
ztoi_p_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoipoisson_early_results_log_normalL"), row.names = 1)
ztoi_p_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoipoisson_early_results_log_normalU"), row.names = 1)

# oiztpoisson
oizt_p_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztpoisson_early_results_point_est"), row.names = 1)
oizt_p_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztpoisson_early_results_normalL"), row.names = 1)
oizt_p_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztpoisson_early_results_normalU"), row.names = 1)
oizt_p_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztpoisson_early_results_log_normalL"), row.names = 1)
oizt_p_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztpoisson_early_results_log_normalU"), row.names = 1)

# ztHurdlepoisson
zthr_p_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlepoisson_early_results_point_est"), row.names = 1)
zthr_p_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlepoisson_early_results_normalL"), row.names = 1)
zthr_p_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlepoisson_early_results_normalU"), row.names = 1)
zthr_p_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlepoisson_early_results_log_normalL"), row.names = 1)
zthr_p_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlepoisson_early_results_log_normalU"), row.names = 1)

# Hurdleztpoisson
hrzt_p_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztpoisson_early_results_point_est"), row.names = 1)
hrzt_p_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztpoisson_early_results_normalL"), row.names = 1)
hrzt_p_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztpoisson_early_results_normalU"), row.names = 1)
hrzt_p_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztpoisson_early_results_log_normalL"), row.names = 1)
hrzt_p_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztpoisson_early_results_log_normalU"), row.names = 1)

# ztoigeom
ztoi_g_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoigeom_early_results_point_est"), row.names = 1)
ztoi_g_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoigeom_early_results_normalL"), row.names = 1)
ztoi_g_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoigeom_early_results_normalU"), row.names = 1)
ztoi_g_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoigeom_early_results_log_normalL"), row.names = 1)
ztoi_g_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoigeom_early_results_log_normalU"), row.names = 1)

# oiztgeom
oizt_g_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztgeom_early_results_point_est"), row.names = 1)
oizt_g_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztgeom_early_results_normalL"), row.names = 1)
oizt_g_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztgeom_early_results_normalU"), row.names = 1)
oizt_g_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztgeom_early_results_log_normalL"), row.names = 1)
oizt_g_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztgeom_early_results_log_normalU"), row.names = 1)

# ztHurdlegeom
zthr_g_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlegeom_early_results_point_est"), row.names = 1)
zthr_g_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlegeom_early_results_normalL"), row.names = 1)
zthr_g_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlegeom_early_results_normalU"), row.names = 1)
zthr_g_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlegeom_early_results_log_normalL"), row.names = 1)
zthr_g_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlegeom_early_results_log_normalU"), row.names = 1)

# Hurdleztgeom
hrzt_g_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztgeom_early_results_point_est"), row.names = 1)
hrzt_g_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztgeom_early_results_normalL"), row.names = 1)
hrzt_g_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztgeom_early_results_normalU"), row.names = 1)
hrzt_g_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztgeom_early_results_log_normalL"), row.names = 1)
hrzt_g_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztgeom_early_results_log_normalU"), row.names = 1)

# ztoinegbin
ztoi_nb_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoinegbin_early_results_point_est"), row.names = 1)
ztoi_nb_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoinegbin_early_results_normalL"), row.names = 1)
ztoi_nb_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoinegbin_early_results_normalU"), row.names = 1)
ztoi_nb_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoinegbin_early_results_log_normalL"), row.names = 1)
ztoi_nb_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztoinegbin_early_results_log_normalU"), row.names = 1)

# oiztnegbin
oizt_nb_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztnegbin_early_results_point_est"), row.names = 1)
oizt_nb_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztnegbin_early_results_normalL"), row.names = 1)
oizt_nb_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztnegbin_early_results_normalU"), row.names = 1)
oizt_nb_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztnegbin_early_results_log_normalL"), row.names = 1)
oizt_nb_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/oiztnegbin_early_results_log_normalU"), row.names = 1)

# ztHurdlenegbin
zthr_nb_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlenegbin_early_results_point_est"), row.names = 1)
zthr_nb_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlenegbin_early_results_normalL"), row.names = 1)
zthr_nb_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlenegbin_early_results_normalU"), row.names = 1)
zthr_nb_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlenegbin_early_results_log_normalL"), row.names = 1)
zthr_nb_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/ztHurdlenegbin_early_results_log_normalU"), row.names = 1)

# Hurdleztnegbin
hrzt_nb_point      <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztnegbin_early_results_point_est"), row.names = 1)
hrzt_nb_norm_l     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztnegbin_early_results_normalL"), row.names = 1)
hrzt_nb_norm_u     <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztnegbin_early_results_normalU"), row.names = 1)
hrzt_nb_log_norm_l <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztnegbin_early_results_log_normalL"), row.names = 1)
hrzt_nb_log_norm_u <- read.csv(paste0(paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/"), "/results/Hurdleztnegbin_early_results_log_normalU"), row.names = 1)
```

```{r cleaning, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
#library(singleRcapture)
# put data in long format
results_data_frame <- data.frame(
  data_generation = rep(c(
    "ztoipoisson", "oiztpoisson", "ztHurdlepoisson", "Hurdleztpoisson",
    "ztoigeom",    "oiztgeom",    "ztHurdlegeom",    "Hurdleztgeom",
    "ztoinegbin",  "oiztnegbin",  "ztHurdlenegbin",  "Hurdleztnegbin"
  ), 500 * c(
    6, 6, 6, 6, 
    7, 7, 7, 7, 
    7, 7, 7, 7
  )),
  data_fitted = rep(
    sapply(list(
      ztoi_p_point, oizt_p_point, zthr_p_point, hrzt_p_point, 
      ztoi_g_point, oizt_g_point, zthr_g_point, hrzt_g_point, 
      ztoi_nb_point, oizt_nb_point, zthr_nb_point,hrzt_nb_point
    ), FUN = colnames) |> unlist(), 
    each = 500
  ),
  point = c(
    ztoi_p_point |> as.vector() |> unlist() |> as.numeric(),
    oizt_p_point |> as.vector() |> unlist() |> as.numeric(),
    zthr_p_point |> as.vector() |> unlist() |> as.numeric(),
    hrzt_p_point |> as.vector() |> unlist() |> as.numeric(),
    ztoi_g_point |> as.vector() |> unlist() |> as.numeric(),
    oizt_g_point |> as.vector() |> unlist() |> as.numeric(),
    zthr_g_point |> as.vector() |> unlist() |> as.numeric(),
    hrzt_g_point |> as.vector() |> unlist() |> as.numeric(),
    ztoi_nb_point |> as.vector() |> unlist() |> as.numeric(),
    oizt_nb_point |> as.vector() |> unlist() |> as.numeric(),
    zthr_nb_point |> as.vector() |> unlist() |> as.numeric(),
    hrzt_nb_point |> as.vector() |> unlist() |> as.numeric()
  ),
  conf_int_normal_lower = c(
    ztoi_p_norm_l |> as.vector() |> unlist() |> as.numeric(),
    oizt_p_norm_l |> as.vector() |> unlist() |> as.numeric(),
    zthr_p_norm_l |> as.vector() |> unlist() |> as.numeric(),
    hrzt_p_norm_l |> as.vector() |> unlist() |> as.numeric(),
    ztoi_g_norm_l |> as.vector() |> unlist() |> as.numeric(),
    oizt_g_norm_l |> as.vector() |> unlist() |> as.numeric(),
    zthr_g_norm_l |> as.vector() |> unlist() |> as.numeric(),
    hrzt_g_norm_l |> as.vector() |> unlist() |> as.numeric(),
    ztoi_nb_norm_l |> as.vector() |> unlist() |> as.numeric(),
    oizt_nb_norm_l |> as.vector() |> unlist() |> as.numeric(),
    zthr_nb_norm_l |> as.vector() |> unlist() |> as.numeric(),
    hrzt_nb_norm_l |> as.vector() |> unlist() |> as.numeric()
  ),
  conf_int_log_normal_lower = c(
    ztoi_p_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    oizt_p_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    zthr_p_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    hrzt_p_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    ztoi_g_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    oizt_g_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    zthr_g_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    hrzt_g_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    ztoi_nb_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    oizt_nb_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    zthr_nb_log_norm_l |> as.vector() |> unlist() |> as.numeric(),
    hrzt_nb_log_norm_l |> as.vector() |> unlist() |> as.numeric()
  ),
  conf_int_normal_upper = c(
    ztoi_p_norm_u |> as.vector() |> unlist() |> as.numeric(),
    oizt_p_norm_u |> as.vector() |> unlist() |> as.numeric(),
    zthr_p_norm_u |> as.vector() |> unlist() |> as.numeric(),
    hrzt_p_norm_u |> as.vector() |> unlist() |> as.numeric(),
    ztoi_g_norm_u |> as.vector() |> unlist() |> as.numeric(),
    oizt_g_norm_u |> as.vector() |> unlist() |> as.numeric(),
    zthr_g_norm_u |> as.vector() |> unlist() |> as.numeric(),
    hrzt_g_norm_u |> as.vector() |> unlist() |> as.numeric(),
    ztoi_nb_norm_u |> as.vector() |> unlist() |> as.numeric(),
    oizt_nb_norm_u |> as.vector() |> unlist() |> as.numeric(),
    zthr_nb_norm_u |> as.vector() |> unlist() |> as.numeric(),
    hrzt_nb_norm_u |> as.vector() |> unlist() |> as.numeric()
  ),
  conf_int_log_normal_upper = c(
    ztoi_p_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    oizt_p_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    zthr_p_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    hrzt_p_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    ztoi_g_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    oizt_g_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    zthr_g_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    hrzt_g_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    ztoi_nb_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    oizt_nb_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    zthr_nb_log_norm_u |> as.vector() |> unlist() |> as.numeric(),
    hrzt_nb_log_norm_u |> as.vector() |> unlist() |> as.numeric()
  )
)
```

General results:

```{r summarisation, out.width = "150%", out.height = "150%"}
summarised_df <- results_data_frame |> 
  group_by(data_generation, data_fitted) |> 
  summarise(mean_point              = mean(point, na.rm = TRUE),
            mean_ci_length_norm     = mean(conf_int_normal_upper - conf_int_normal_lower, na.rm = TRUE),
            coverage_ci_norm        = mean((conf_int_normal_lower < 1000) & (1000 < conf_int_normal_upper), na.rm = TRUE),
            mean_ci_length_log_norm = mean(conf_int_log_normal_upper - conf_int_log_normal_lower, na.rm = TRUE),
            coverage_ci_log_norm    = mean((conf_int_log_normal_lower < 1000) & (1000 < conf_int_log_normal_upper), na.rm = TRUE),
            succesful_fits          = mean(!is.na(point)))
print(summarised_df, n=20)

pp <- summarised_df |>
  subset(succesful_fits < 1) |>
  as.data.frame() |> 
  mutate(data_generation = ordered(data_generation)) |>
  ggplot(aes(y = succesful_fits, x = data_fitted)) +
  geom_point() +
  facet_wrap(~data_generation, scales = c("free_x"), ncol = 3) + 
  ylab("Fitted proportion") +
  xlab("Model fitted") +
  ggtitle("Proportion of succesfully fitted models by true distribution of counts")

pp
```

Visualising outliers (i.e. when estimated regression parameters tend to boundary):

```{r outliers, out.width = "150%", out.height = "150%"}
outliers <- results_data_frame |>
  subset(!is.na(point)) |>
  subset(point > 5000) |> 
  group_by(data_generation, data_fitted) |>
  summarise(n = n()) |>
  ggplot(aes(x = data_fitted, weight = n)) +
  geom_bar() +
  facet_wrap(~ data_generation, scales = c("free_x")) + 
  ylab("Number of outliers") +
  xlab("Model fitted") +
  ggtitle("Exreme outliers (estimate > 5 * true size) by true distribution of counts")

outliers
```

## Point estimates

Results for counts generated by ztoipoisson:

```{r ztoipoisson, out.width = "150%", out.height = "150%"}
p1 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztoipoisson")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p1
```

Summary statistics after excluding outliers:
```{r ztoipoisson_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztoipoisson")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by oiztpoisson:

```{r oiztpoisson, out.width = "150%", out.height = "150%"}
p2 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "oiztpoisson")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p2
```

Summary statistics after excluding outliers:
```{r oiztpoisson_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "oiztpoisson")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by ztHurdlepoisson:

```{r ztHurdlepoisson, out.width = "150%", out.height = "150%"}
p3 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztHurdlepoisson")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p3
```

Summary statistics after excluding outliers:
```{r ztHurdlepoisson_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztHurdlepoisson")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by hurdleztpoisson:

```{r Hurdleztpoisson, out.width = "150%", out.height = "150%"}
p4 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "Hurdleztpoisson")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p4
```

Summary statistics after excluding outliers:
```{r Hurdleztpoisson_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "Hurdleztpoisson")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by ztoigeom:

```{r ztoigeom, out.width = "150%", out.height = "150%"}
p5 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztoigeom")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p5
```

Summary statistics after excluding outliers:
```{r ztoigeom_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztoigeom")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by oiztgeom:

```{r oiztgeom, out.width = "150%", out.height = "150%"}
p6 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "oiztgeom")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p6
```

Summary statistics after excluding outliers:
```{r oiztgeom_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "oiztgeom")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by ztHurdlegeom:

```{r ztHurdlegeom, out.width = "150%", out.height = "150%"}
p7 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztHurdlegeom")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p7
```

Summary statistics after excluding outliers:
```{r ztHurdlegeom_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztHurdlegeom")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by hurdleztgeom:

```{r Hurdleztgeom, out.width = "150%", out.height = "150%"}
p8 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "Hurdleztgeom")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p8
```

Summary statistics after excluding outliers:
```{r Hurdleztgeom_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "Hurdleztgeom")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by ztoinegbin:

```{r ztoinegbin, out.width = "150%", out.height = "150%"}
p9 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztoinegbin")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p9
```

Summary statistics after excluding outliers:
```{r ztoinegbin_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztoinegbin")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by oiztnegbin:

```{r oiztnegbin, out.width = "150%", out.height = "150%"}
p10 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "oiztnegbin")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p10
```

Summary statistics after excluding outliers:
```{r oiztnegbin_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "oiztnegbin")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by ztHurdlenegbin:

```{r ztHurdlenegbin, out.width = "150%", out.height = "150%"}
p11 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztHurdlenegbin")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p11
```

Summary statistics after excluding outliers:
```{r ztHurdlenegbin_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "ztHurdlenegbin")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

Results for counts generated by hurdleztnegbin:

```{r Hurdleztnegbin, out.width = "150%", out.height = "150%"}
p12 <- results_data_frame |>
  subset(!is.na(point) & (data_generation == "Hurdleztnegbin")) |>
  subset(point < 5000) |>
  ggplot(aes(x = data_fitted, y = point)) +
  geom_jitter(alpha = 0.05, shape = 1) + 
  geom_violin(alpha = 0.8, draw_quantiles = 1:9 / 10, scale = "width") +
  stat_summary(fun = function(x) mean(x, na.rm = TRUE), geom = "point") + 
  geom_hline(yintercept = 1000, linetype="dashed", color = "red") +
  ylab("Point estimate") +
  xlab("Model fitted")

p12
```

Summary statistics after excluding outliers:
```{r Hurdleztnegbin_summary_stats}
results_data_frame |>
  subset(!is.na(point) & (data_generation == "Hurdleztnegbin")) |>
  subset(point < 5000) |>
  group_by(data_fitted) |>
  summarise(bias = mean(point - 1000),
            rel_bias = mean(point - 1000) / 1000,
            MSE = mean((point - 1000)^2),
            MAE = mean(abs(point - 1000)),
            coverage_normal = mean((conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000)),
            coverage_log_normal = mean((conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000))) |>
  print(n=20L)
```

```{r saving, echo=FALSE}
dir <- paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/")
ggsave(plot = pp, filename = paste0(dir, "/figures/fitted_proportion.png"), width = 9, height = 12)
ggsave(plot = p1, filename = paste0(dir, "/figures/ztoipoisson.png"), width = 9, height = 12)
ggsave(plot = p2, filename = paste0(dir, "/figures/oiztpoisson.png"), width = 9, height = 12)
ggsave(plot = p3, filename = paste0(dir, "/figures/ztHurdlepoisson.png"), width = 9, height = 12)
ggsave(plot = p4, filename = paste0(dir, "/figures/Hurdleztpoisson.png"), width = 9, height = 12)
ggsave(plot = p5, filename = paste0(dir, "/figures/ztoigeom.png"), width = 9, height = 12)
ggsave(plot = p6, filename = paste0(dir, "/figures/oiztgeom.png"), width = 9, height = 12)
ggsave(plot = p7, filename = paste0(dir, "/figures/ztHurdlegeom.png"), width = 9, height = 12)
ggsave(plot = p8, filename = paste0(dir, "/figures/Hurdleztgeom.png"), width = 9, height = 12)
ggsave(plot = p9, filename = paste0(dir, "/figures/ztoinegbin.png"), width = 9, height = 12)
ggsave(plot = p10, filename = paste0(dir, "/figures/oiztnegbin.png"), width = 9, height = 12)
ggsave(plot = p11, filename = paste0(dir, "/figures/ztHurdlenegbin.png"), width = 9, height = 12)
ggsave(plot = p12, filename = paste0(dir, "/figures/Hurdleztnegbin.png"), width = 9, height = 12)
```

## Confidence intervals

### Normal

Exact binomial tests for coverage of lognormal confindence intervals with $H_0:p=0.95, H_1:p\neq0.95$:

```{r coverage_normal1}
dd <- results_data_frame |>
  subset(!is.na(point)) |>
  subset(point < 5000) |>
  mutate(covr_norm = (conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000),
         covr_log  = (conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000)) |>
  group_by(data_generation, data_fitted) |>
  summarise(n = n(),
            mean = mean(covr_norm, na.rm = TRUE))

dd <- cbind(dd, p_value = NA, lower = NA, upper = NA, signif = NA)

for (x in 1:NROW(dd)) {
  jj <- binom.test(x = as.numeric(dd[x, 4]) * as.integer(dd[x, 3]), n = as.integer(dd[x, 3]), p = .95)
  # this jj object has some very weird interactions with the rest of R ecosystem
  dd[x, 5] <- jj$p.value |> as.numeric()
  dd[x, 6] <- jj[[4]][1]
  dd[x, 7] <- jj[[4]][2]
  dd[x, 8] <- ifelse(dd[x, 5] < .001, "***", ifelse(dd[x, 5] < .01, "**", ifelse(dd[x, 5] < .05, "*", ifelse(dd[x, 5] < .1, ".", ""))))
}

dd |> 
  mutate(p_value = round(p_value, digits = 4),
         lower   = round(lower, digits = 4),
         upper   = round(upper, digits = 4)) |>
  print(n = NROW(dd))

## show only those that have high p value or have better coverage
dd |>
  filter(p_value > .05 | mean > .95) |>
  mutate(p_value = round(p_value, digits = 4),
         lower   = round(lower, digits = 4),
         upper   = round(upper, digits = 4)) |>
  print(n = NROW(dd))
```

Visual results with confidence intervals:

```{r coverage_normal2, out.width = "150%", out.height = "150%"}
qq1 <- dd |>
  ggplot(aes(x = data_fitted)) +
  facet_wrap(~ data_generation, scales = c("free_x"), ncol = 3) +
  geom_point(aes(y = mean), colour = "navy", cex = 2) +
  geom_errorbar(aes(ymin = lower, ymax = upper), colour = "navy") +
  ggtitle("Empirical coverage of studentized confidence intervals by true distribution of counts") +
  xlab("Fitted distribution") +
  ylab("Coverage")

qq1
```

Average sizes of confidence intervals:

```{r sizes_normal, out.width = "150%", out.height = "150%"}
qq2 <- results_data_frame |>
  subset(!is.na(point)) |>
  subset(point < 5000) |>
  group_by(data_generation, data_fitted) |>
  summarise(len = mean(conf_int_normal_upper - conf_int_normal_lower, na.rm = TRUE)) |>
  ggplot(aes(x = data_fitted, weight = len)) +
  geom_bar() +
  facet_wrap(~ data_generation, scales = c("free_x"), ncol = 3) +
  ylab("Average length") +
  xlab("Fitted distribution") +
  ggtitle("Empirical size of studentized confidence intervals by true distribution of counts")

qq2
```

### Logormal

Exact binomial tests for coverage of normal confindence intervals with $H_0:p=0.95, H_1:p\neq0.95$:

```{r coverage_log_normal1, out.width = "150%", out.height = "150%"}
dd <- results_data_frame |>
  subset(!is.na(point)) |>
  subset(point < 5000) |>
  mutate(covr_norm = (conf_int_normal_lower < 1000) & (conf_int_normal_upper > 1000),
         covr_log  = (conf_int_log_normal_lower < 1000) & (conf_int_log_normal_upper > 1000)) |>
  group_by(data_generation, data_fitted) |>
  summarise(n = n(),
            mean = mean(covr_log, na.rm = TRUE))

dd <- cbind(dd, p_value = NA, lower = NA, upper = NA, signif = NA)

for (x in 1:NROW(dd)) {
  jj <- binom.test(x = as.numeric(dd[x, 4]) * as.integer(dd[x, 3]), n = as.integer(dd[x, 3]), p = .95)
  # this jj object has some very weird interactions with the rest of R ecosystem
  dd[x, 5] <- jj$p.value |> as.numeric()
  dd[x, 6] <- jj[[4]][1]
  dd[x, 7] <- jj[[4]][2]
  dd[x, 8] <- ifelse(dd[x, 5] < .001, "***", ifelse(dd[x, 5] < .01, "**", ifelse(dd[x, 5] < .05, "*", ifelse(dd[x, 5] < .1, ".", ""))))
}

dd |> 
  mutate(p_value = round(p_value, digits = 4),
         lower   = round(lower, digits = 4),
         upper   = round(upper, digits = 4)) |>
  print(n = NROW(dd))

## show only those that have high p value or have better coverage
dd |>
  filter(p_value > .05 | mean > .95) |>
  mutate(p_value = round(p_value, digits = 4),
         lower   = round(lower, digits = 4),
         upper   = round(upper, digits = 4)) |>
  print(n = NROW(dd))
```

Visual results with confidence intervals:

```{r coverage_log_normal2, out.width = "150%", out.height = "150%"}
qq3 <- dd |>
  ggplot(aes(x = data_fitted)) +
  facet_wrap(~ data_generation, scales = c("free_x"), ncol = 3) +
  geom_point(aes(y = mean), colour = "navy", cex = 2) +
  geom_errorbar(aes(ymin = lower, ymax = upper), colour = "navy") +
  ggtitle("Empirical coverage of log normal confidence intervals by true distribution of counts") +
  xlab("Fitted distribution") +
  ylab("Coverage")

qq3
```

Average sizes of confidence intervals:

```{r sizes_log_normal, out.width = "150%", out.height = "150%"}
qq4 <- results_data_frame |>
  subset(!is.na(point)) |>
  subset(point < 5000) |>
  group_by(data_generation, data_fitted) |>
  summarise(len = mean(conf_int_log_normal_upper - conf_int_log_normal_lower, na.rm = TRUE)) |>
  ggplot(aes(x = data_fitted, weight = len)) +
  geom_bar() +
  facet_wrap(~ data_generation, scales = "free", ncol = 3) +
  ylab("Average length") +
  xlab("Fitted distribution") +
  ggtitle("Empirical size of log normal confidence intervals by true distribution of counts")

qq4
```

```{r saving2, echo=FALSE}
dir <- paste(strsplit(getwd(), split = "/")[[1]][1:5], collapse = "/")
ggsave(plot = qq1, filename = paste0(dir, "/figures/confint_normal_coverage.png"), width = 10.5, height = 14)
ggsave(plot = qq2, filename = paste0(dir, "/figures/confint_normal_size.png"), width = 10.5, height = 14)
ggsave(plot = qq3, filename = paste0(dir, "/figures/confint_log_normal_coverage.png"), width = 10.5, height = 14)
ggsave(plot = qq4, filename = paste0(dir, "/figures/confint_log_normal_size.png"), width = 10.5, height = 14)
ggsave(plot = outliers, filename = paste0(dir, "/figures/outliers.png"), width = 10.5, height = 14)
```